02-clean_data

### 2024-02-10 scripts/02-clean_data.qmd
Upload Clean data

---
title: "Cleaned Data"
format: html
---

---
title: "Inaction We Trust"
author: "Adrien Fillon"
date: "27/01/2021"
format: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

@@

# setting formatting options
options(scipen=999, digits =3)

# Study 2

```{r study 2, echo=FALSE}
#DOWNLOAD DATA
data2 <- read.csv("inactionwetrust_study2.csv",sep = ";" )
```

```{r descriptives2}
# CLEAN DATA

# data2 <- data2[-c(1:2),]
## remove variable descriptions + practice data

>>>>

---
title: "02-clean_data"
format: html
---
```{r}
#### Preamble ####
# Purpose: Replicate the "Inaction We Trust" data cleaning by "Adrien Fillon"
# Author: Hari Lee Robledo, Sky Suh and Francesca Ye
# Date: 10 February 2024
# Pre-requisites: none
```

#### Workspace setup ####
```{r setup, include=FALSE}
# Code referenced from: https://osf.io/kzf3x
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

@@

# setting formatting options
options(scipen=999, digits =3)
```

#### Read Data ####
```{r study 2, echo=FALSE}
#DOWNLOAD DATA
data2 <- read.csv("study_2_raw_data.csv",sep = ";" )
```

#### Clean Data ####
```{r descriptives2}
# Code referenced from: https://osf.io/kzf3x
## remove variable descriptions + practice data
